---
title: "Meta analysis"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

```{r}

# dependencies
library(tidyverse)
library(timesavers)
library(lme4)
library(effects)
library(metafor)
library(patchwork)
library(lme4)

# source for raincloud plots
source("geom_flat_violin.R")

# disable scientific notation
options(scipen = 999) 

# knitr output for html
options(knitr.table.format = "html")


# custom functions --------------------

# fit models to individual experiments and extract an effect of interest
fit_lm_model_and_extract_effect <- function(data, experiment_n, formula, effect) {
  require(tidyverse)
  
  fit <- data %>%
    dplyr::filter(experiment == experiment_n) %>%
    lm(formula = formula, 
       data = .)
  
  results <- 
    summary(fit)$coefficients %>%
    as.data.frame() %>%
    rownames_to_column(var = "Effect") %>%
    dplyr::filter(Effect == effect) %>%
    mutate(Experiment = experiment_n,
           yi = Estimate,       # effect size
           vi = `Std. Error`^2) # convert SE to variance
  
  return(results)
}

# fit models to individual experiments and extract an effect of interest
fit_glmer_model_and_extract_effect <- function(data, experiment_n, formula, effect) {
  require(tidyverse)
  
  fit <- data %>%
    dplyr::filter(experiment == experiment_n) %>%
    glmer(formula = formula, 
          family = binomial(link = "logit"),
          data = .)
  
  results <- 
    summary(fit)$coefficients %>%
    as.data.frame() %>%
    rownames_to_column(var = "Effect") %>%
    dplyr::filter(Effect == effect) %>%
    mutate(Experiment = experiment_n,
           yi = Estimate,       # effect size
           vi = `Std. Error`^2) # convert SE to variance
  
  return(results)
}

# meta analyse and plot
meta_analysis_workflow <- function(data, effect_size_label, reference_line, exp_estimates = FALSE) {
  require(timesavers)
  require(tidyverse)
  require(metafor)
  
  # fit random effects model 
  fitted_model <- 
    rma(yi, vi,
        data = data,
        slab = Experiment)
  
  # model predictions
  meta_analysis_results <-
    predict(fitted_model, digits = 5) %>%
    as.data.frame() %>%
    gather() %>%
    round_df(3) %>%
    dplyr::rename(metric = key,
                  estimate = value) %>%
    mutate(metric = dplyr::recode(metric,
                                  "pred" = paste0("Meta analysed ", effect_size_label),
                                  "ci.lb" = "95% CI lower",
                                  "ci.ub" = "95% CI upper",
                                  "cr.lb" = "95% CR lower",
                                  "cr.ub" = "95% CR upper"))
  
  meta_analysis_results_as_probabilities_text <- NULL
  
  # conditionally exponentiate estimates if converting log odds to odds ratios
  if(exp_estimates == TRUE) {
    meta_analysis_results <- meta_analysis_results %>%
      mutate(estimate = round(exp(estimate), 3))
  }
  
  # summarize results
  meta_analysis_results_text <- 
    paste0("k = ", fitted_model$k, ", ", effect_size_label, " = ", meta_analysis_results$estimate[1],
           # dynamic indexing of some values as different models return variables in different locations, but relative location is reliable
           ", 95% CI [",  meta_analysis_results$estimate[length(meta_analysis_results$estimate)-3],  
           ", ",          meta_analysis_results$estimate[length(meta_analysis_results$estimate)-2], 
           "], 95% CR [", meta_analysis_results$estimate[length(meta_analysis_results$estimate)-1], 
           ", ",          meta_analysis_results$estimate[length(meta_analysis_results$estimate)], 
           "], p = ",     signif(2*pnorm(-abs(fitted_model$zval)), digits = 1))  # p value from z score
  
  meta_analysis_results_as_probabilities_text <- 
    paste0("k = ", fitted_model$k, ", Probability = ", meta_analysis_results$estimate[1],
           # dynamic indexing of some values as different models return variables in different locations, but relative location is reliable
           ", 95% CI [",  round(meta_analysis_results$estimate[length(meta_analysis_results$estimate)-3] /
             (1 + meta_analysis_results$estimate[length(meta_analysis_results$estimate)-3]), 3), 
           ", ",          round(meta_analysis_results$estimate[length(meta_analysis_results$estimate)-2] / 
             (1 + meta_analysis_results$estimate[length(meta_analysis_results$estimate)-2]), 3),
           "], 95% CR [", round(meta_analysis_results$estimate[length(meta_analysis_results$estimate)-1] /
             (1 + meta_analysis_results$estimate[length(meta_analysis_results$estimate)-1]), 3),
           ", ",          round(meta_analysis_results$estimate[length(meta_analysis_results$estimate)] / 
             (1 + meta_analysis_results$estimate[length(meta_analysis_results$estimate)]), 3),
           "], p = ",     signif(2*pnorm(-abs(fitted_model$zval)), digits = 1))  # p value from z score

  heterogeneity_test_results_text <- 
    paste0("Q(df = ",     fitted_model$k - 1, ") = ", round(fitted_model$QE, 2), 
           ", p = ",      ifelse(fitted_model$QEp < 0.001, "< .001", as.character(round(fitted_model$pval, 3))),
           ", tau^2 = ",  round(fitted_model$tau2, 2), 
           ", I^2 = ",    round(fitted_model$I2, 2),
           ", H^2 = ",    round(fitted_model$H2, 2))
  
  # forest plot
  if (exp_estimates == TRUE) {
    transformation <- exp
  } else { 
    transformation <- NULL
  }
  
  forest_plot <- forest(fitted_model,
                        xlab = effect_size_label,
                        addcred = TRUE,
                        atransf = transformation,
                        refline = reference_line)
  
  return(list(fitted_model = fitted_model, 
              meta_analysis_results = meta_analysis_results,
              meta_analysis_results_text = meta_analysis_results_text,
              meta_analysis_results_as_probabilities_text = meta_analysis_results_as_probabilities_text,
              heterogeneity_test_results_text = heterogeneity_test_results_text,
              forest_plot = forest_plot))
}


# get data

combined_participant_level_data <- read.csv("data/combined_participant_level_data.csv")
combined_trial_level_data <- read.csv("data/combined_trial_level_data.csv")

```

# AMP effect ~ IA AMP influence rate

amp_type	amp_domain

absolute IA amp effect?


```{r}

reshaped_data <- combined_participant_level_data %>%
  dplyr::select(unique_id, experiment, influence_rate, AMP_effect_positive_negative, AMP_effect_obama_trump) %>%
  gather(AMP_type, AMP_effect, c("AMP_effect_positive_negative", "AMP_effect_obama_trump")) %>%
  na.omit

formula <- as.formula("AMP_effect ~ influence_rate")
effect  <- "influence_rate"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_amp <- rbind(
  fit_lm_model_and_extract_effect(data = reshaped_data, experiment_n = 2, formula = formula, effect = effect),
  fit_lm_model_and_extract_effect(data = reshaped_data, experiment_n = 3, formula = formula, effect = effect),
  fit_lm_model_and_extract_effect(data = reshaped_data, experiment_n = 5, formula = formula, effect = effect)
) 

# meta analyse results
meta_results_amp <- meta_analysis_workflow(data              = results_for_meta_analysis_amp,
                                           effect_size_label = "Beta",
                                           reference_line    = 0)

```

- Meta analysis: `r meta_results_amp$meta_analysis_results_text`
- Heterogeneity tests: `r meta_results_amp$heterogeneity_test_results_text`

```{r}

# library(lme4)
# library(sjPlot)
# 
# combined_trial_level_data <- combined_trial_level_data %>%
#   mutate(influenced_inverted = abs(influenced - 1))
# 
# summary <- combined_trial_level_data %>%
#   group_by(experiment, unique_id) %>%
#   dplyr::summarize(perc_influenced = mean(influenced)) %>%
#   ungroup()
# 
# ggplot(summary, aes(perc_influenced, group = as.factor(experiment), fill = as.factor(experiment))) +
#   geom_density(alpha = 0.4, adjust = 0.8) +
#   scale_fill_viridis_d()


library(ggExtra)

p <- ggplot(reshaped_data, 
            aes(influence_rate, abs(AMP_effect))) +
  geom_point(alpha = 0.3, position = position_jitter()) +
  geom_smooth(method = "lm") +
  scale_color_viridis_d(end = 0.8) +
  theme_classic()

p2 <- ggMarginal(p, 
                 type = "histogram", 
                 margins = "both", 
                 size = 3)

```

```{r fig.height=5, fig.width=5}

grid::grid.newpage()
grid::grid.draw(p2)

```

# IA-AMP analyses

## Participant level analyses

### IA-AMP influence rate

```{r}

formula <- as.formula("influence_rate ~ 1")
effect  <- "(Intercept)"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_inf <- rbind(
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 1, 
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 2, 
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 3, 
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 4, 
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 5, 
                                  formula = formula, 
                                  effect = effect)
)

# meta analyse results
meta_results_inf <- meta_analysis_workflow(data              = results_for_meta_analysis_inf, 
                                           effect_size_label = "Influence rate",
                                           reference_line    = 0)

```

- Meta analysis: `r meta_results_inf$meta_analysis_results_text`
- Heterogeneity tests: `r meta_results_inf$heterogeneity_test_results_text`

### IA-AMP effect ~ IA-AMP influence rate 

absolute IA amp effect?

random effect candidates:

- experiment, ia amp domain, ia amp type, 

```{r}

formula <- as.formula("IA_AMP_effect_positive_negative ~ influence_rate")
effect  <- "influence_rate"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_2 <- rbind(
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, experiment_n = 1, formula = formula, effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, experiment_n = 2, formula = formula, effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, experiment_n = 3, formula = formula, effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, experiment_n = 4, formula = formula, effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, experiment_n = 5, formula = formula, effect = effect)
)

# meta analyse results
meta_results_2 <- meta_analysis_workflow(data              = results_for_meta_analysis_2, 
                                         effect_size_label = "Beta",
                                         reference_line    = 0)

```

- Meta analysis: `r meta_results_2$meta_analysis_results_text`
- Heterogeneity tests: `r meta_results_2$heterogeneity_test_results_text`

```{r}

# library(lme4)
# library(sjPlot)
# 
# combined_trial_level_data <- combined_trial_level_data %>%
#   mutate(influenced_inverted = abs(influenced - 1))
# 
# summary <- combined_trial_level_data %>%
#   group_by(experiment, unique_id) %>%
#   dplyr::summarize(perc_influenced = mean(influenced)) %>%
#   ungroup()
# 
# ggplot(summary, aes(perc_influenced, group = as.factor(experiment), fill = as.factor(experiment))) +
#   geom_density(alpha = 0.4, adjust = 0.8) +
#   scale_fill_viridis_d()


library(ggExtra)

p <- ggplot(combined_participant_level_data, 
            aes(influence_rate, abs(IA_AMP_effect_positive_negative))) +
  geom_point(alpha = 0.3, position = position_jitter()) +
  geom_smooth(method = "lm") +
  scale_color_viridis_d(end = 0.8) +
  theme_classic()

p2 <- ggMarginal(p, 
                 type = "histogram", 
                 margins = "both", 
                 size = 3)

```

```{r fig.height=5, fig.width=5}

grid::grid.newpage()
grid::grid.draw(p2)

```

#### in progress - Multivariate meta option

exp 4 has two IA-AMPs

need to revisit data processing first

```{r}

# # reshape data
# data_temp <- results_for_meta_analysis_2 %>%
#   bind_cols(Domain = c("(Generic valence)",
#                        "(Politics)",
#                        "(Generic valence)")) %>%
#   rename(V = vi)
# 
# # fit
# fit <- rma.mv(yi     = yi, 
#               V      = V,
#               random = ~ 1 | Experiment/Domain,
#               data   = data_temp,
#               slab   = paste(Experiment, Domain))
# 
# # plot
# forest(fit,
#        xlab = "Beta",
#        addcred = TRUE,
#        refline = 0)
# 
# fit

```

## Trial level analyses

### IA-AMP influence rate ~ 1

```{r}

formula <- as.formula("influenced ~ 1 + (1 | unique_id)")
effect  <- "(Intercept)"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_4 <- rbind(
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 1, 
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 2, 
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 3, 
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 4, 
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 5, 
                                     formula = formula, 
                                     effect = effect)
)

# meta analyse results
meta_results_4 <- meta_analysis_workflow(data              = results_for_meta_analysis_4, 
                                         effect_size_label = "OR",
                                         reference_line    = NULL, 
                                         exp_estimates     = TRUE) # exponentiate log odds to odds ratios

```

- N participants = `r nrow(combined_participant_level_data)`
- N IA-AMP trials = `r nrow(combined_trial_level_data)`
- Meta analysis (probabilities rather than odds ratios): `r meta_results_4$meta_analysis_results_as_probabilities_text`
- Heterogeneity tests: `r meta_results_4$heterogeneity_test_results_text`

### IA-AMP effect ~ influence

```{r}

formula <- as.formula("rating ~ prime_type * influenced + (1 | unique_id)")
effect  <- "prime_typePositive:influenced"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_5 <- rbind(
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 1, 
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 2, 
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 3, 
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 4, 
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 5, 
                                     formula = formula, 
                                     effect = effect)
)

# meta analyse results
meta_results_5 <- meta_analysis_workflow(data              = results_for_meta_analysis_5, 
                                         effect_size_label = "OR",
                                         reference_line    = NULL, 
                                         exp_estimates     = TRUE) # exponentiate log odds to odds ratios

```

- N participants = `r nrow(combined_participant_level_data)`
- N IA-AMP trials = `r nrow(combined_trial_level_data)`
- Meta analysis: `r meta_results_5$meta_analysis_results_text`
- Heterogeneity tests: `r meta_results_5$heterogeneity_test_results_text`

```{r fig.height=11, fig.width=9}

# fit combined model
model_combined <- glmer(rating ~ prime_type * influenced + (1 | unique_id) + (1 | experiment), 
                        family = binomial(link = "logit"),
                        data = combined_trial_level_data)

# predictions
model_combined_predicted_effects <- 
  as.data.frame(effect("prime_type:influenced", model_combined, xlevels = 50)) %>%
  round_df(2) %>%
  mutate(prime_type = fct_relevel(prime_type, "Negative", "Positive"))

# Plot 1 -  quantiles (10ths) of interaction effect 
p1 <- 
  ggplot(data = model_combined_predicted_effects,
         aes(x = prime_type, y = fit, colour = influenced, group = influenced)) +
  geom_line() +
  ylab("Mean evaluation on IA-AMP") +
  xlab("Prime type") +
  #scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  scale_colour_viridis_c(direction = -1) +
  theme_classic() + 
  labs(colour = "Proportion of\ninfluenced trials") +
  scale_y_continuous(breaks = c(0, 0.25, 0.50, 0.75, 1.00), 
                     labels = c("(Negative) 0.00", "0.25", "0.50", "0.75", "(Positive) 1.00"), 
                     limits = c(0, 1))


# Plot 2 - differences between influenced and non influenced trials

## add these probabilities back to the original data frame (omitting missing values) 
predictions <- combined_trial_level_data %>%
  dplyr::select(prime_type, influenced, unique_id,  experiment) %>%
  na.omit %>%
  mutate(prob = predict(model_combined, type = c("response")),
         `Influence of prime\non evaluation of target` = dplyr::recode(influenced, 
                                                                       "0" = "Uninfluenced trials",
                                                                       "1" = "Influenced trials"),
         prime_type = fct_relevel(prime_type, "Negative", "Positive"))

# plot
p2 <- 
  ggplot(data = predictions, 
         aes(x = as.factor(prime_type), 
             y = prob,
             fill = `Influence of prime\non evaluation of target`,
             color = `Influence of prime\non evaluation of target`)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0),
                   adjust = 2,
                   alpha = .8) +
  geom_point(position = position_jitter(width = .15), 
             size = 0.25, 
             alpha = 0.8) +
  scale_colour_viridis_d(begin = 0.3, end = 0.7) +
  scale_fill_viridis_d(begin = 0.3, end = 0.7) +
  coord_flip() +
  theme_classic() +
  xlab("Prime type") +
  ylab("Evaluation on IA-AMP") +
  scale_y_continuous(breaks = c(0, 0.25, 0.50, 0.75, 1.00), 
                     labels = c("0.00\n(Negative)", "0.25", "0.50", "0.75", "1.00\n(Positive)"), 
                     limits = c(0, 1)) + 
  labs(color = "Influence of prime on evaluation of target") + 
  labs(name = "Influence of prime on evaluation of target") +
  labs(fill = "Influence of prime on evaluation of target")

# combined plots
p1 + p2 + plot_layout(ncol = 1)

```



