---
title: "Meta analysis"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

```{r}

# dependencies
library(tidyverse)
library(timesavers)
library(lme4)
library(effects)
library(metafor)
library(patchwork)
library(ggExtra)
library(sjPlot)
library(kableExtra)
library(knitr)
library(patchwork)
library(ggridges)

# source for raincloud plots
source("geom_flat_violin.R")

# disable scientific notation
options(scipen = 999) 

# knitr output for html
options(knitr.table.format = "html")


# custom functions --------------------

zscore_to_p <- function(z){
  2*pnorm(-abs(z))
}

# fit models to individual experiments and extract an effect of interest
fit_lm_model_and_extract_effect <- function(data, experiment_n, formula, effect, 
                                            IA_AMP_domain_name = NULL,
                                            AMP_domain_name = NULL) {
  require(tidyverse)
  
  if (!is.null(IA_AMP_domain_name)) {
    
    fit <- data %>%
      dplyr::filter(experiment == experiment_n & 
                      IA_AMP_domain == IA_AMP_domain_name) %>%
      lm(formula = formula, 
         data = .)
    
    results <- 
      summary(fit)$coefficients %>%
      as.data.frame() %>%
      rownames_to_column(var = "Effect") %>%
      dplyr::filter(Effect == effect) %>%
      mutate(Experiment = experiment_n,
             IA_AMP_domain = IA_AMP_domain_name,
             yi = Estimate,       # effect size
             vi = `Std. Error`^2) # convert SE to variance
    
  } else if (!is.null(AMP_domain_name)) {
    
    fit <- data %>%
      dplyr::filter(experiment == experiment_n & 
                      AMP_domain == AMP_domain_name) %>%
      lm(formula = formula, 
         data = .)
    
    results <- 
      summary(fit)$coefficients %>%
      as.data.frame() %>%
      rownames_to_column(var = "Effect") %>%
      dplyr::filter(Effect == effect) %>%
      mutate(Experiment = experiment_n,
             AMP_domain = AMP_domain_name,
             yi = Estimate,       # effect size
             vi = `Std. Error`^2) # convert SE to variance
    
  }
  
  return(results)
}

# fit models to individual experiments and extract an effect of interest
fit_glmer_model_and_extract_effect <- function(data, experiment_n, formula, effect, domain_name = NULL) {
  require(tidyverse)
  
  if (!is.null(domain_name)) {
    
    fit <- data %>%
      dplyr::filter(experiment == experiment_n & 
                      domain == domain_name) %>%
      glmer(formula = formula, 
            family = binomial(link = "logit"),
            data = .)
    
    results <- 
      summary(fit)$coefficients %>%
      as.data.frame() %>%
      rownames_to_column(var = "Effect") %>%
      dplyr::filter(Effect == effect) %>%
      mutate(Experiment = experiment_n,
             domain = domain_name,
             yi = Estimate,       # effect size
             vi = `Std. Error`^2) # convert SE to variance
    
  } else {
    
    fit <- data %>%
      dplyr::filter(experiment == experiment_n) %>%
      glmer(formula = formula, 
            family = binomial(link = "logit"),
            data = .)
    
    results <- 
      summary(fit)$coefficients %>%
      as.data.frame() %>%
      rownames_to_column(var = "Effect") %>%
      dplyr::filter(Effect == effect) %>%
      mutate(Experiment = experiment_n,
             yi = Estimate,       # effect size
             vi = `Std. Error`^2) # convert SE to variance
  }
  
  return(results)
}


# get data
combined_participant_level_data <- read.csv("data/combined_participant_level_data.csv") 
combined_trial_level_data       <- read.csv("data/combined_trial_level_data.csv")  %>%
  mutate(influenced = as.logical(influenced))

```

e3# Total participants after exclusions

```{r}

combined_participant_level_data %>%
  distinct(unique_id) %>%
  dplyr::count() %>%
  kable()

```

# Does influence rate predict the magnitude of (IA)AMP effects?

## IA-AMP

### Participant level

#### Main effect

IA-AMP effect ~ IA-AMP influence rate 

Absolute IA-AMP effects.

```{r}

formula <- as.formula("abs(IA_AMP_effect) ~ influence_rate")
effect  <- "influence_rate"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_1 <- rbind(
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 1, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 2, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 3, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 4, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 4, 
                                  IA_AMP_domain_name = "Politics",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 5, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect)
)

```

```{r}

# reshape data
data_temp <- results_for_meta_analysis_1 %>%
  dplyr::rename(V = vi)

# fit
fit <- rma.mv(yi     = yi,
              V      = V,
              random = ~ 1 | Experiment/IA_AMP_domain,
              data   = data_temp,
              slab   = paste(Experiment, IA_AMP_domain))

# plot
forest(fit,
       xlab = "Beta",
       addcred = TRUE,
       refline = 0)

# convert to OR, show CR
predict(fit) %>%
  as.data.frame() %>%
  round_df(2) %>%
  mutate(p = zscore_to_p(fit$zval))

```

##### Plot

```{r fig.height=5, fig.width=5}

temp_data <- combined_participant_level_data %>%
  select(experiment, IA_AMP_domain, IA_AMP_effect, influence_rate)

ggplot(temp_data, 
       aes(influence_rate, IA_AMP_effect, color = IA_AMP_domain)) +
  geom_smooth(method = "lm") +
  scale_color_viridis_d(end = 0.7, begin = 0.3) +
  theme_classic() +
  xlab("IA-AMP influence-awareness rate") +
  ylab("Absolute magnitude of IA-AMP effect") +
  labs(color = "Domain") + 
  labs(name = "Domain") +
  labs(fill = "Domain") + 
  theme(legend.position = c(0.3, .8))

```

#### Intercept effect

IA-AMP effect ~ 1

Absolute IA-AMP effects.

```{r}

formula <- as.formula("abs(IA_AMP_effect) ~ 1")
effect  <- "(Intercept)"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_1b <- rbind(
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 1, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 2, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 3, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 4, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 4, 
                                  IA_AMP_domain_name = "Politics",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 5, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect)
)

```

```{r}

# reshape data
data_temp <- results_for_meta_analysis_1b %>%
  dplyr::rename(V = vi)

# fit
fitb <- rma.mv(yi     = yi,
               V      = V,
               random = ~ 1 | Experiment/IA_AMP_domain,
               data   = data_temp,
               slab   = paste(Experiment, IA_AMP_domain))

# plot
forest(fitb,
       xlab = "Beta",
       addcred = TRUE,
       refline = 0)

# convert to OR, show CR
predict(fitb) %>%
  as.data.frame() %>%
  round_df(2) %>%
  mutate(p = zscore_to_p(fitb$zval))

```

### Trial level

#### Interaction effect

Positive-negative IA-AMPs only (i.e., no Politics IA-AMP), as trial level data reveals the magnitude of the AMP effect but not the absolute magnitude. When there are meaningful individual differences between the positive and negative category (i.e., the Politics IA-AMP but not the positive-negative IA-AMP), the native trial level AMP effects between groups conceal the absolute magnitudes. As such, it is only meaningful to meta analyze the positive-negative IA-AMP effects.  

```{r}

formula <- as.formula("rating ~ prime_type * influenced + (1 | unique_id)")
effect  <- "prime_typePositive:influencedTRUE"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_2 <- rbind(
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 1, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 2, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 3, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 4, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 5, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect)
)

```

```{r}

# reshape data
data_temp <- results_for_meta_analysis_2 %>%
  dplyr::rename(V = vi)

# fit
fit <- rma.mv(yi     = yi,
              V      = V,
              random = ~ 1 | Experiment/domain,
              data   = data_temp,
              slab   = paste(Experiment, domain))

# plot
forest(fit,
       xlab = "Odds Ratio",
       addcred = TRUE,
       refline = 1,
       atransf = exp)

# convert to OR, show CR
OR <- predict(fit) %>%
  as.data.frame() %>%
  exp() %>%
  select(-se) %>%
  round_df(2) 

## print as odds ratios
OR %>%
  mutate(p = zscore_to_p(fit$zval))

```

Convert to cohen's d

```{r}

OR_to_d(OR) %>%
  round_df(2)

```

##### Plot

```{r fig.height=5, fig.width=5}

# fit combined model
data_for_mod_plot <- 
  combined_trial_level_data %>%
  mutate(influenced = as.numeric(influenced))

model_2 <- glmer(rating ~ prime_type * influenced + (1 | experiment/unique_id),
                 family = binomial(link = "logit"),
                 data = data_for_mod_plot)

# predictions
model_2_predicted_effects <- 
  as.data.frame(effect(term    = "prime_type:influenced", 
                       mod     = model_2, 
                       xlevels = 101)) %>%
  round_df(2) %>%
  mutate(prime_type = fct_relevel(prime_type, "Negative", "Positive"))

# Plot 1 -  quantiles (10ths) of interaction effect 
p2 <- ggplot(data = model_2_predicted_effects,
             aes(x = prime_type, y = fit, colour = influenced, group = influenced)) +
  geom_line() +
  ylab("Mean evaluation on IA-AMP") +
  xlab("Prime type") +
  #scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  scale_colour_viridis_c(direction = -1) +
  theme_classic() + 
  labs(colour = "Proportion of\ninfluence-aware\ntrials") +
  scale_y_continuous(breaks = c(0, 0.25, 0.50, 0.75, 1.00), 
                     labels = c("0.00\n(Negative) ", "0.25", "0.50", "0.75", "1.00\n(Positive) "), 
                     limits = c(0, 1)) + 
  theme(legend.position = c(0.85, 0.30))

p2

save(p2, file = "data/p2.RData")

```

```{r fig.height=5, fig.width=6.5}

# Plot 2 - differences between influenced and non influenced trials

## add these probabilities back to the original data frame (omitting missing values) 
predictions <- combined_trial_level_data %>%
  dplyr::select(prime_type, influenced, unique_id,  experiment) %>%
  mutate(influenced = as.numeric(influenced)) %>%
  na.omit %>%
  mutate(prob = predict(model_2, type = c("response")),
         `Influence of prime\non evaluation of target` = dplyr::recode(influenced, 
                                                                       "0" = "Non-influence aware trials",
                                                                       "1" = "Influence aware trials"),
         prime_type = fct_relevel(prime_type, "Negative", "Positive"))

# plot
ggplot(data = predictions, 
       aes(x = `Influence of prime\non evaluation of target`, 
           y = prob,
           fill = as.factor(prime_type),
           color = as.factor(prime_type))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0),
                   adjust = 2,
                   alpha = .8) +
  geom_point(position = position_jitter(width = .15), 
             size = 0.25, 
             alpha = 0.8) +
  scale_colour_viridis_d(begin = 0.3, end = 0.7) +
  scale_fill_viridis_d(begin = 0.3, end = 0.7) +
  coord_flip() +
  theme_classic() +
  xlab("Influence-awareness of prime on evaluation of target") +
  ylab("Evaluation on IA-AMP") +
  scale_y_continuous(breaks = c(0, 0.25, 0.50, 0.75, 1.00), 
                     labels = c("0.00\n(Negative)", "0.25", "0.50", "0.75", "1.00\n(Positive)"), 
                     limits = c(0, 1)) + 
  labs(color = "Prime type") + 
  labs(name = "Prime type") +
  labs(fill = "Prime type")

```

```{r fig.height=5, fig.width=6.5}

# plot 3: interaction
plot_model(model_2, 
           type = "pred", 
           terms = c("influenced", "prime_type")) +
  theme_classic() +
  xlab("Influence-awareness rate") +
  ylab("Evaluation on IA-AMP") +
  scale_color_viridis_d(begin = 0.3, end = 0.7) +
  scale_fill_viridis_d(begin = 0.3, end = 0.7) + 
  labs(color = "Prime type") + 
  labs(name = "Prime type") +
  labs(fill = "Prime type") +
  ggtitle("") +
  xlim(0,1) +
  ylim(0,1)

```

#### Main effect

Positive-negative IA-AMPs only (i.e., no Politics IA-AMP), as trial level data reveals the magnitude of the AMP effect but not the absolute magnitude. When there are meaningful individual differences between the positive and negative category (i.e., the Politics IA-AMP but not the positive-negative IA-AMP), the native trial level AMP effects between groups conceal the absolute magnitudes. As such, it is only meaningful to meta analyze the positive-negative IA-AMP effects.  

```{r}

formula <- as.formula("rating ~ prime_type + (1 | unique_id)")
effect  <- "prime_typePositive"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_2b <- rbind(
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 1, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 2, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 3, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 4, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 5, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect)
)

```

```{r}

# reshape data
data_temp <- results_for_meta_analysis_2b %>%
  dplyr::rename(V = vi)

# fit
fitb <- rma.mv(yi     = yi,
               V      = V,
               random = ~ 1 | Experiment/domain,
               data   = data_temp,
               slab   = paste(Experiment, domain))

# plot
forest(fitb,
       xlab = "Odds Ratio",
       addcred = TRUE,
       refline = 1,
       atransf = exp)

# convert to OR, show CR
ORb <- predict(fitb) %>%
  as.data.frame() %>%
  exp() %>%
  select(-se) %>%
  round_df(2) 

## print as odds ratios
ORb %>%
  mutate(p = zscore_to_p(fit$zval))

```

Convert to cohen's d

```{r}

OR_to_d(ORb) %>%
  round_df(2)

```

## AMP effect ~ IA-AMP influence rate

### Participant level 

#### Main effect

AMP effect ~ IA-AMP influence rate

Absolute AMP effects.

```{r}

formula <- as.formula("abs(AMP_effect) ~ influence_rate")
effect  <- "influence_rate"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_3 <- rbind(
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 2, 
                                  AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 3, 
                                  AMP_domain_name = "Politics",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 5, 
                                  AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect)
) 

```

```{r}

# reshape data
data_temp <- results_for_meta_analysis_3 %>%
  dplyr::rename(V = vi)

# fit
fit <- rma.mv(yi     = yi,
              V      = V,
              random = ~ 1 | Experiment/AMP_domain,
              data   = data_temp,
              slab   = paste(Experiment, AMP_domain))

# plot
forest(fit,
       xlab = "Beta",
       addcred = TRUE,
       refline = 0)

# convert to OR, show CR
predict(fit) %>%
  as.data.frame() %>%
  round_df(2) %>%
  mutate(p = zscore_to_p(fit$zval))

```

##### Plot

```{r fig.height=5, fig.width=5}

temp_data <- combined_participant_level_data %>%
  filter((experiment == 2 & AMP_domain == "Generic valence") |
           (experiment == 3 & AMP_domain == "Politics") |
           (experiment == 5 & AMP_domain == "Generic valence")) %>%
  select(experiment, AMP_domain, IA_AMP_domain, influence_rate, AMP_effect) %>%
  mutate(prediction_type = ifelse(AMP_domain == IA_AMP_domain, "Same domain", "Different domain"))

p3 <- ggplot(temp_data, 
             aes(influence_rate, AMP_effect, color = prediction_type)) +
  geom_smooth(method = "lm") +
  scale_color_viridis_d(end = 0.7, begin = 0.3) +
  theme_classic() +
  xlab("IA-AMP influence-awareness rate\n(Completed second)") +
  ylab("Absolute magnitude of AMP effect\n(Completed first)") +
  labs(color = "Domains assessed by\nthe IA-AMP vs. AMP") + 
  labs(name = "Domains assessed by\nthe IA-AMP vs. AMP") +
  labs(fill = "Domains assessed by\nthe IA-AMP vs. AMP") + 
  theme(legend.position = c(0.3, .8))

p3

save(p3, file = "data/p3.RData")

```

#### Intercept effect

AMP effect ~ IA-AMP influence rate

Absolute AMP effects.

```{r}

formula <- as.formula("abs(AMP_effect) ~ 1")
effect  <- "(Intercept)"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_3b <- rbind(
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 2, 
                                  AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 3, 
                                  AMP_domain_name = "Politics",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 5, 
                                  AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect)
) 

```

```{r}

# reshape data
data_temp <- results_for_meta_analysis_3b %>%
  dplyr::rename(V = vi)

# fit
fitb <- rma.mv(yi     = yi,
               V      = V,
               random = ~ 1 | Experiment/AMP_domain,
               data   = data_temp,
               slab   = paste(Experiment, AMP_domain))

# plot
forest(fitb,
       xlab = "Beta",
       addcred = TRUE,
       refline = 0)

# convert to OR, show CR
predict(fitb) %>%
  as.data.frame() %>%
  round_df(2) %>%
  mutate(p = zscore_to_p(fit$zval))

```

# IA-AMP influence rate

Combination analysis due to severe bimodality.

Participant level

## Distribution

```{r fig.height=5, fig.width=5}

# Distribution
p4 <- ggplot(combined_participant_level_data, aes(influence_rate)) +
  geom_density(adjust = .4, fill = 1, alpha = .8) +
  #geom_histogram(fill = 1, alpha = .8, bins = 30) +
  #geom_histogram(fill = 1, alpha = .8, bins = 100) +
  theme_classic() +
  xlab("Influence-awareness rate") +
  ylab("Distribution density")

p4

save(p4, file = "data/p4.RData")

```

```{r}

N <- nrow(combined_participant_level_data)

combined_participant_level_data %>%
  mutate(influence_rate_quintiles = ifelse(influence_rate <= .20, 1, 
                                           ifelse(influence_rate <= .40, 2, 
                                                  ifelse(influence_rate <= .60, 3, 
                                                         ifelse(influence_rate <= .80, 4, 
                                                                ifelse(influence_rate <= 1.00, 5, NA))))),
         influence_rate_quintiles = as.factor(influence_rate_quintiles)) %>%
  dplyr::count(influence_rate_quintiles) %>%
  mutate(percent = round(n/N, 2)) %>%
  kable()

combined_participant_level_data %>%
  mutate(influence_rate_categories = ifelse(influence_rate <= .05, "almost none", 
                                            ifelse(influence_rate >= 0.95, "almost all", "some")),
         influence_rate_categories = as.factor(influence_rate_categories)) %>%
  dplyr::count(influence_rate_categories) %>%
  mutate(percent = round(n/N, 2)) %>%
  kable()

combined_participant_level_data %>%
  summarize(median_influence_rate = median(influence_rate),
            mad_influence_rate = mad(influence_rate)) %>%
  kable()

```

# Combine plots

```{r fig.height=16.2, fig.width=6}

# get plot from exp 4
load("../Experiment 4/analysis/p1.RData")

p_combined <- p1 + p2 + p3 + p4 + plot_layout(ncol = 1)

p_combined

save(p_combined, file = "plots/p_combined.RData")

```


