---
title: "Meta analysis"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

```{r}

# dependencies
library(tidyverse)
library(timesavers)
library(lme4)
library(effects)
library(metafor)
library(patchwork)
library(ggExtra)
library(sjPlot)
library(kableExtra)
library(knitr)

# source for raincloud plots
source("geom_flat_violin.R")

# disable scientific notation
options(scipen = 999) 

# knitr output for html
options(knitr.table.format = "html")


# custom functions --------------------

zscore_to_p <- function(z){
  2*pnorm(-abs(z))
}

# fit models to individual experiments and extract an effect of interest
fit_lm_model_and_extract_effect <- function(data, experiment_n, formula, effect, 
                                            IA_AMP_domain_name = NULL,
                                            AMP_domain_name = NULL) {
  require(tidyverse)
  
  if (!is.null(IA_AMP_domain_name)) {
    
    fit <- data %>%
      dplyr::filter(experiment == experiment_n & 
                      IA_AMP_domain == IA_AMP_domain_name) %>%
      lm(formula = formula, 
         data = .)
    
    results <- 
      summary(fit)$coefficients %>%
      as.data.frame() %>%
      rownames_to_column(var = "Effect") %>%
      dplyr::filter(Effect == effect) %>%
      mutate(Experiment = experiment_n,
             IA_AMP_domain = IA_AMP_domain_name,
             yi = Estimate,       # effect size
             vi = `Std. Error`^2) # convert SE to variance
    
  } else if (!is.null(AMP_domain_name)) {
    
    fit <- data %>%
      dplyr::filter(experiment == experiment_n & 
                      AMP_domain == AMP_domain_name) %>%
      lm(formula = formula, 
         data = .)
    
    results <- 
      summary(fit)$coefficients %>%
      as.data.frame() %>%
      rownames_to_column(var = "Effect") %>%
      dplyr::filter(Effect == effect) %>%
      mutate(Experiment = experiment_n,
             AMP_domain = AMP_domain_name,
             yi = Estimate,       # effect size
             vi = `Std. Error`^2) # convert SE to variance
    
  }
  
  return(results)
}

# fit models to individual experiments and extract an effect of interest
fit_glmer_model_and_extract_effect <- function(data, experiment_n, formula, effect, domain_name = NULL) {
  require(tidyverse)
  
  if (!is.null(domain_name)) {
    
    fit <- data %>%
      dplyr::filter(experiment == experiment_n & 
                      domain == domain_name) %>%
      glmer(formula = formula, 
            family = binomial(link = "logit"),
            data = .)
    
    results <- 
      summary(fit)$coefficients %>%
      as.data.frame() %>%
      rownames_to_column(var = "Effect") %>%
      dplyr::filter(Effect == effect) %>%
      mutate(Experiment = experiment_n,
             domain = domain_name,
             yi = Estimate,       # effect size
             vi = `Std. Error`^2) # convert SE to variance
    
  } else {
    
    fit <- data %>%
      dplyr::filter(experiment == experiment_n) %>%
      glmer(formula = formula, 
            family = binomial(link = "logit"),
            data = .)
    
    results <- 
      summary(fit)$coefficients %>%
      as.data.frame() %>%
      rownames_to_column(var = "Effect") %>%
      dplyr::filter(Effect == effect) %>%
      mutate(Experiment = experiment_n,
             yi = Estimate,       # effect size
             vi = `Std. Error`^2) # convert SE to variance
  }
  
  return(results)
}


# get data
combined_participant_level_data <- read.csv("data/combined_participant_level_data.csv")
combined_trial_level_data       <- read.csv("data/combined_trial_level_data.csv") 

```

# Does influence rate predict the magnitude of (IA)AMP effects?

## IA-AMP

### Participant level

IA-AMP effect ~ IA-AMP influence rate 

Absolute IA-AMP effects.

```{r}

formula <- as.formula("abs(IA_AMP_effect) ~ influence_rate")
effect  <- "influence_rate"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_1 <- rbind(
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 1, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 2, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 3, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 4, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 4, 
                                  IA_AMP_domain_name = "Politics",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 5, 
                                  IA_AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect)
)

```

```{r}

# reshape data
data_temp <- results_for_meta_analysis_1 %>%
  dplyr::rename(V = vi)

# fit
fit <- rma.mv(yi     = yi,
              V      = V,
              random = ~ 1 | Experiment/IA_AMP_domain,
              data   = data_temp,
              slab   = paste(Experiment, IA_AMP_domain))

# plot
forest(fit,
       xlab = "Beta",
       addcred = TRUE,
       refline = 0)

# convert to OR, show CR
predict(fit) %>%
  as.data.frame() %>%
  round_df(2) %>%
  mutate(p = zscore_to_p(fit$zval))

```

#### Plot

```{r fig.height=5, fig.width=5}

temp_data <- combined_participant_level_data %>%
  select(experiment, IA_AMP_domain, IA_AMP_effect, influence_rate)

ggplot(temp_data, 
       aes(influence_rate, IA_AMP_effect, color = IA_AMP_domain)) +
  geom_smooth(method = "lm") +
  scale_color_viridis_d(end = 0.7, begin = 0.3) +
  theme_classic() +
  xlab("IA-AMP influence-awareness rate") +
  ylab("Absolute magnitude of IA-AMP effect") +
  labs(color = "Domain") + 
  labs(name = "Domain") +
  labs(fill = "Domain") + 
  theme(legend.position = c(0.3, .8))
  
```

### Trial level

```{r}

formula <- as.formula("rating ~ prime_type * influenced + (1 | unique_id)")
effect  <- "prime_typePositive:influenced"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_2 <- rbind(
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 1, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 2, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 3, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 4, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 4, 
                                     domain_name = "Politics",
                                     formula = formula, 
                                     effect = effect),
  fit_glmer_model_and_extract_effect(data = combined_trial_level_data, 
                                     experiment_n = 5, 
                                     domain_name = "Generic valence",
                                     formula = formula, 
                                     effect = effect)
)

```

```{r}

# reshape data
data_temp <- results_for_meta_analysis_2 %>%
  dplyr::rename(V = vi)

# fit
fit <- rma.mv(yi     = yi,
              V      = V,
              random = ~ 1 | Experiment/domain,
              data   = data_temp,
              slab   = paste(Experiment, domain))

# plot
forest(fit,
       xlab = "Odds Ratio",
       addcred = TRUE,
       refline = 1,
       atransf = exp)

# convert to OR, show CR
OR <- predict(fit) %>%
  as.data.frame() %>%
  exp() %>%
  select(-se) %>%
  round_df(2) 

## print as odds ratios
OR %>%
  mutate(p = zscore_to_p(fit$zval))

```

Convert to cohen's d

```{r}

OR_to_d(OR) %>%
  round_df(2)

```

#### Plot

```{r fig.height=5, fig.width=6.5}

# # fit combined model
# model_2 <- glmer(rating ~ prime_type * influenced + (1 | experiment/unique_id) + (1 | domain), 
#                  family = binomial(link = "logit"),
#                  data = combined_trial_level_data)
# 
# save(model_2, file = "model_2.Rdata")
load("model_2.RData")

# predictions
model_2_predicted_effects <- 
  as.data.frame(effect("prime_type:influenced", model_2, xlevels = 50)) %>%
  round_df(2) %>%
  mutate(prime_type = fct_relevel(prime_type, "Negative", "Positive"))

# Plot 1 -  quantiles (10ths) of interaction effect 
ggplot(data = model_2_predicted_effects,
         aes(x = prime_type, y = fit, colour = influenced, group = influenced)) +
  geom_line() +
  ylab("Mean evaluation on IA-AMP") +
  xlab("Prime type") +
  #scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1)) +
  scale_colour_viridis_c(direction = -1) +
  theme_classic() + 
  labs(colour = "Proportion of\ninfluence-aware\ntrials") +
  scale_y_continuous(breaks = c(0, 0.25, 0.50, 0.75, 1.00), 
                     labels = c("(Negative) 0.00", "0.25", "0.50", "0.75", "(Positive) 1.00"), 
                     limits = c(0, 1)) + 
  theme(legend.position = c(0.85, 0.30))

```

```{r fig.height=5, fig.width=6.5}

# Plot 2 - differences between influenced and non influenced trials

## add these probabilities back to the original data frame (omitting missing values) 
predictions <- combined_trial_level_data %>%
  dplyr::select(prime_type, influenced, unique_id,  experiment) %>%
  na.omit %>%
  mutate(prob = predict(model_2, type = c("response")),
         `Influence of prime\non evaluation of target` = dplyr::recode(influenced, 
                                                                       "0" = "Uninfluenced trials",
                                                                       "1" = "Influenced trials"),
         prime_type = fct_relevel(prime_type, "Negative", "Positive"))

# plot
ggplot(data = predictions, 
         aes(x = `Influence of prime\non evaluation of target`, 
             y = prob,
             fill = as.factor(prime_type),
             color = as.factor(prime_type))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0),
                   adjust = 2,
                   alpha = .8) +
  geom_point(position = position_jitter(width = .15), 
             size = 0.25, 
             alpha = 0.8) +
  scale_colour_viridis_d(begin = 0.3, end = 0.7) +
  scale_fill_viridis_d(begin = 0.3, end = 0.7) +
  coord_flip() +
  theme_classic() +
  xlab("Influence-awareness of prime on evaluation of target") +
  ylab("Evaluation on IA-AMP") +
  scale_y_continuous(breaks = c(0, 0.25, 0.50, 0.75, 1.00), 
                     labels = c("0.00\n(Negative)", "0.25", "0.50", "0.75", "1.00\n(Positive)"), 
                     limits = c(0, 1)) + 
  labs(color = "Prime type") + 
  labs(name = "Prime type") +
  labs(fill = "Prime type")

```

```{r fig.height=5, fig.width=6.5}

# plot 3: interaction
plot_model(model_2, 
           type = "pred", 
           terms = c("influenced", "prime_type")) +
  theme_classic() +
  xlab("Influence-awareness rate") +
  ylab("Evaluation on IA-AMP") +
  scale_color_viridis_d(begin = 0.3, end = 0.7) +
  scale_fill_viridis_d(begin = 0.3, end = 0.7) + 
  labs(color = "Prime type") + 
  labs(name = "Prime type") +
  labs(fill = "Prime type") +
  ggtitle("") +
  xlim(0,1) +
  ylim(0,1)

```

## AMP effect ~ IA-AMP influence rate

### Participant level 

AMP effect ~ IA-AMP influence rate

Absolute AMP effects.

```{r}

formula <- as.formula("AMP_effect ~ influence_rate")
effect  <- "influence_rate"

# apply models to individual experiments, extract results for key effect
results_for_meta_analysis_3 <- rbind(
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 2, 
                                  AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 3, 
                                  AMP_domain_name = "Politics",
                                  formula = formula, 
                                  effect = effect),
  fit_lm_model_and_extract_effect(data = combined_participant_level_data, 
                                  experiment_n = 5, 
                                  AMP_domain_name = "Generic valence",
                                  formula = formula, 
                                  effect = effect)
) 

```

```{r}

# reshape data
data_temp <- results_for_meta_analysis_3 %>%
  dplyr::rename(V = vi)

# fit
fit <- rma.mv(yi     = yi,
              V      = V,
              random = ~ 1 | Experiment/AMP_domain,
              data   = data_temp,
              slab   = paste(Experiment, AMP_domain))

# plot
forest(fit,
       xlab = "Beta",
       addcred = TRUE,
       refline = 0)

# convert to OR, show CR
predict(fit) %>%
  as.data.frame() %>%
  round_df(2) %>%
  mutate(p = zscore_to_p(fit$zval))

```

#### Plot

```{r fig.height=5, fig.width=5}

temp_data <- combined_participant_level_data %>%
  filter((experiment == 2 & AMP_domain == "Generic valence") |
           (experiment == 3 & AMP_domain == "Politics") |
           (experiment == 5 & AMP_domain == "Generic valence")) %>%
  select(experiment, AMP_domain, IA_AMP_domain, influence_rate, AMP_effect) %>%
  mutate(prediction_type = ifelse(AMP_domain == IA_AMP_domain, "Same domain", "Different domain"))

ggplot(temp_data, 
       aes(influence_rate, AMP_effect, color = prediction_type)) +
  geom_smooth(method = "lm") +
  scale_color_viridis_d(end = 0.7, begin = 0.3) +
  theme_classic() +
  xlab("IA-AMP influence-awareness rate\n(Completed second)") +
  ylab("Absolute magnitude of AMP effect\n(Completed first)") +
  labs(color = "Domains assessed by\nthe IA-AMP vs. AMP") + 
  labs(name = "Domains assessed by\nthe IA-AMP vs. AMP") +
  labs(fill = "Domains assessed by\nthe IA-AMP vs. AMP") + 
  theme(legend.position = c(0.3, .8))

```

# IA-AMP influence rate

Combination analysis due to severe bimodality.

Participant level

## Distribution

```{r fig.height=5, fig.width=5}

# Distribution
ggplot(combined_participant_level_data, aes(influence_rate)) +
  geom_density(adjust = .4, fill = 1, alpha = .8) +
  #geom_histogram(fill = 1, alpha = .8, bins = 30) +
  #geom_histogram(fill = 1, alpha = .8, bins = 100) +
  theme_classic() +
  xlab("Influence-awareness rate") +
  ylab("Distribution density")

```

```{r}

N <- nrow(combined_participant_level_data)

combined_participant_level_data %>%
  mutate(influence_rate_quintiles = ifelse(influence_rate <= .20, 1, 
                                           ifelse(influence_rate <= .40, 2, 
                                                  ifelse(influence_rate <= .60, 3, 
                                                         ifelse(influence_rate <= .80, 4, 
                                                                ifelse(influence_rate <= 1.00, 5, NA))))),
         influence_rate_quintiles = as.factor(influence_rate_quintiles)) %>%
  dplyr::count(influence_rate_quintiles) %>%
  mutate(percent = round(n/N, 2)) %>%
  kable()

combined_participant_level_data %>%
  mutate(influence_rate_categories = ifelse(influence_rate <= .05, "almost none", 
                                           ifelse(influence_rate >= 0.95, "almost all", "some")),
         influence_rate_categories = as.factor(influence_rate_categories)) %>%
  dplyr::count(influence_rate_categories) %>%
  mutate(percent = round(n/N, 2)) %>%
  kable()

combined_participant_level_data %>%
  summarize(median_influence_rate = median(influence_rate),
            mad_influence_rate = mad(influence_rate)) %>%
  kable()

```
