---
title: "Meta analysis"
author: "Ian Hussey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

```{r}

# dependencies
library(tidyverse)
library(lme4)
library(effects)
library(metafor)
library(patchwork)
library(sjPlot)
library(knitr)
library(kableExtra)
library(patchwork)
library(diptest)
library(multimode)
library(performance)

# disable scientific notation
options(scipen = 999) 

# knitr output for html
options(knitr.table.format = "html")

# get data
data_participant_level <- 
  read.csv("../data/data_combined_participant_level.csv") %>%
  mutate(AMP_effect = AMP_effect*-1,
         IA_AMP_effect = IA_AMP_effect*-1,
         experiment = as.factor(experiment),
         abs_AMP_effect = abs(AMP_effect),
         abs_IA_AMP_effect = abs(IA_AMP_effect),
         abs_IA_AMP_effect_uninfluenced_trials = abs(IA_AMP_uninfluenced_effect), 
         abs_IA_AMP_effect_influenced_trials = abs(IA_AMP_influenced_effect))

data_trial_level_valence_ia_amp  <- 
  read.csv("../data/data_combined_trial_level.csv")  %>%
  mutate(Awareness = ifelse(influenced == 0, "Non-aware trials", ifelse(influenced == 1, "Aware trials", NA)),
         Awareness = fct_relevel(Awareness, "Non-aware trials", "Aware trials"),
         prime_type = as.factor(prime_type)) %>%
  rownames_to_column(var = "unique_row_name") %>%
  group_by(experiment, IA_AMP_domain, unique_id, influenced, prime_type) %>%
  mutate(trial_number = row_number(),
         max_trials_per_block = max(trial_number)) %>%
  ungroup() %>%
  filter(IA_AMP_domain == "Valence")

```

# Total participants after exclusions

```{r}

data_participant_level %>%
  distinct(unique_id) %>%
  dplyr::count() %>%
  kable()

```

# Descriptive stats 

## AMP effects

```{r}

data_participant_level %>%
  select(experiment,
         AMP_domain, 
         AMP_effect) %>%
  filter(AMP_domain == "Valence") %>%
  group_by(experiment, 
           AMP_domain) %>%
  dplyr::summarize(M_absolute_AMP_effect = mean(abs(AMP_effect), na.rm = TRUE),
                   SD_absolute_AMP_effect = sd(abs(AMP_effect), na.rm = TRUE)) %>%
  drop_na() %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() %>%  # print nicer looking table
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

## IA-AMP effects

```{r}

data_participant_level %>%
  select(experiment,
         IA_AMP_domain, 
         IA_AMP_effect, 
         IA_AMP_uninfluenced_effect, 
         IA_AMP_influenced_effect) %>%
  filter(IA_AMP_domain == "Valence") %>%
  gather(effect_type, IA_AMP_effect, c(IA_AMP_effect, IA_AMP_uninfluenced_effect, IA_AMP_influenced_effect)) %>%
  group_by(experiment, IA_AMP_domain, effect_type) %>%
  dplyr::summarize(M_absolute_AMP_effect = mean(abs(IA_AMP_effect), na.rm = TRUE),
                   SD_absolute_AMP_effect = sd(abs(IA_AMP_effect), na.rm = TRUE)) %>%
  mutate_if(is.numeric, round, digits = 2) %>%
  kable() %>%  # print nicer looking table
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Does influence rate predict the magnitude of (IA)AMP effects?

## Participant level

### IA-AMP effect ~ IA-AMP influence_rate

IA-AMP effect ~ IA-AMP influence rate

Absolute IA-AMP effects

```{r}

fit_participant_level_ia_amp <- 
  lmer(abs_IA_AMP_effect ~ influence_rate + (1 | experiment), 
       data = data_participant_level)

tab_model(fit_participant_level_ia_amp, 
          show.std = TRUE,
          col.order = c("est", "ci", "std.est", "std.ci", "p"),
          string.est = "B",
          string.ci = "CI",
          string.std = "Std.Beta",
          string.std_ci = "CI",
          emph.p = FALSE,
          ci.hyphen = ", ")

r2_nakagawa(fit_participant_level_ia_amp, by_group = TRUE)

```

### AMP effect ~ IA-AMP influence rate

AMP effect ~ IA-AMP influence rate

Absolute AMP effects

```{r}

fit_participant_level_amp <- 
  lmer(abs_AMP_effect ~ influence_rate + (1 | experiment), 
       data = data_participant_level)

tab_model(fit_participant_level_amp, 
          show.std = TRUE,
          col.order = c("est", "ci", "std.est", "std.ci", "p"),
          string.est = "B",
          string.ci = "CI",
          string.std = "Std.Beta",
          string.std_ci = "CI",
          emph.p = FALSE,
          ci.hyphen = ", ")

r2_nakagawa(fit_participant_level_amp, by_group = TRUE)

```

### Combined plot

```{r fig.height=8.5, fig.width=6}

plot_ia_amp <- 
  data_participant_level %>%  
  mutate(IA_AMP_domain = fct_rev(IA_AMP_domain)) %>% 
  ggplot(aes(influence_rate, abs_IA_AMP_effect, color = experiment, linetype = IA_AMP_domain)) +
  geom_smooth(method = "lm", alpha = 0.0, fullrange = TRUE) +
  ylim(0,1) +
  xlim(0,1) + 
  theme_classic() +
  xlab("Awareness rate") +
  ylab("IA-AMP effect") +
  scale_color_viridis_d(begin = 0.1, end = 0.9) +
  guides(color = guide_legend(title = "Experiment"),
         linetype = guide_legend(title = "Domain"))

plot_amp <- 
  data_participant_level %>%
  mutate(AMP_domain = fct_rev(AMP_domain)) %>% 
  ggplot(aes(influence_rate, abs_AMP_effect, color = experiment, linetype = AMP_domain)) +
  geom_smooth(method = "lm", alpha = 0.0, fullrange = TRUE) +
  ylim(0,1) +
  xlim(0,1) + 
  theme_classic() +
  xlab("Awareness rate") +
  ylab("AMP effect") +
  scale_color_viridis_d(begin = 0.1, end = 0.9) +
  guides(color = guide_legend(title = "Experiment"),
         linetype = guide_legend(title = "Domain"))

# combine
plot_participant_level <- plot_amp / plot_ia_amp

# print 
plot_participant_level

# save object
write_rds(plot_participant_level, "models/plot_participant_level.rds", compress = "gz")

# save pdf
ggsave(filename  = "plot_participant_level.pdf",
       plot      = plot_participant_level,
       device    = "pdf",
       # path      = NULL,
       # dpi       = 300,
       units     = "in",
       width     = 5.0,
       height    = 7.25,
       limitsize = TRUE)

```

## Trial level

Positive-negative IA-AMPs only (i.e., no Politics IA-AMP), as trial level data reveals the magnitude of the AMP effect but not the absolute magnitude. When there are meaningful individual differences between the positive and negative category (i.e., the Politics IA-AMP but not the positive-negative IA-AMP), the native trial level AMP effects between groups conceal the absolute magnitudes. As such, it is only meaningful to meta analyze the positive-negative IA-AMP effects.  

```{r}

#fig.height=3, fig.width=7

# fit model
if(file.exists("models/fit_trial_level.rds")){
  
  fit_trial_level <- read_rds("models/fit_trial_level.rds")
  
} else {
  
  fit_trial_level <- 
    glmer(rating ~ Awareness * prime_type + (1 | unique_id) + (1 | experiment),
          family = binomial(link = "logit"),
          data = data_trial_level_valence_ia_amp)
  
  dir.create("models")
  write_rds(fit_trial_level, path = "models/fit_trial_level.rds", compress = "gz")
  
}

# table
tab_model(fit_trial_level, 
          col.order = c("est", "ci", "p"),
          string.est = "OR",
          string.ci = "CI",
          emph.p = FALSE,
          ci.hyphen = ", ")

r2_nakagawa(fit_trial_level, by_group = TRUE)

# plot
plot_trial_level <- 
  plot_model(fit_trial_level, type = "int") +
  scale_color_viridis_d(begin = 0.3, end = 0.7) +
  theme_classic() +
  ggtitle("") +
  xlab("Awareness") +
  ylab("Evaluation") +
  scale_y_continuous(limits = c(0, 1)) +
  #coord_flip() + 
  labs(color = "Prime type") +
  guides(color = guide_legend(reverse = TRUE)) + 
  scale_x_discrete(limits = c("Non-aware trials", "Aware trials"), 
                   expand = expand_scale(add = 0.65))

# print
plot_trial_level

# save object
write_rds(plot_trial_level, "models/plot_trial_level.rds", compress = "gz")

# save pdf
ggsave(filename  = "plot_trial_level.pdf",
       plot      = plot_trial_level,
       device    = "pdf",
       # path      = NULL,
       # dpi       = 300,
       units     = "in",
       width     = 4.75,
       height    = 3.75,
       limitsize = TRUE)

```

# Awareness rate

Combination analysis due to severe bimodality.

Mann et al. (2019) specifically argued that their modifications should reduce the bimodality of AMP effects, i.e., that there should be distributional differences between the two samples (IA-AMPs employing the standard stimuli and task format vs a Mann et all IA-AMP).

## Visual inspection

```{r fig.height=2.5, fig.width=5}

data_IA_AMP_types <- data_participant_level %>%
  mutate(IA_AMP_type = ifelse(experiment == 6, "Mann et al. (2019) modifications", "Standard IA-AMP")) %>%
  select(IA_AMP_type, experiment, influence_rate)

plot_influence_rate <- 
  ggplot(data_IA_AMP_types, aes(influence_rate, fill = fct_rev(IA_AMP_type))) +
  geom_density(adjust = .5, alpha = 0.5) +
  theme_classic() +
  scale_fill_viridis_d(begin = 0.3, end = 0.7) +
  xlab("Awareness") +
  ylab("Distribution density") +
  guides(fill = guide_legend(title = "IA-AMP type")) + 
  theme(legend.position = c(0.7, 0.8))

plot_influence_rate

# save pdf
ggsave(filename  = "plot_influence_rate.pdf",
       plot      = plot_influence_rate,
       device    = "pdf",
       # path      = NULL,
       # dpi       = 300,
       units     = "in",
       width     = 5,
       height    = 3,
       limitsize = TRUE)

# faceted by experiment
plot_influence_rate_by_experiment <- 
  ggplot(data_IA_AMP_types, aes(influence_rate)) +
  geom_density(adjust = .5, alpha = 0.5) +
  theme_classic() +
  scale_fill_viridis_d(begin = 0.3, end = 0.7) +
  xlab("Awareness") +
  ylab("Distribution density") +
  theme(legend.position = c(0.7, 0.8)) +
  facet_wrap(~experiment)

plot_influence_rate_by_experiment

# save pdf
ggsave(filename  = "plot_influence_rate_by_experiment.pdf",
       plot      = plot_influence_rate_by_experiment,
       device    = "pdf",
       # path      = NULL,
       # dpi       = 300,
       units     = "in",
       width     = 5,
       height    = 3,
       limitsize = TRUE)

```

## Test of unimodality

Hartigans' Dip Tests (H0 = unimodality)

### All data 

```{r}

dip.test(data_IA_AMP_types %>% 
           pull(influence_rate)) 

```

### Subset of standard (non Mann et al) IA-AMPs 

```{r}

dip.test(data_IA_AMP_types %>% 
           filter(IA_AMP_type == "Standard") %>% 
           pull(influence_rate)) 

```

### Subset of Mann et al. IA-AMPs 

```{r}

dip.test(data_IA_AMP_types %>% 
           filter(IA_AMP_type == "Mann et al. (2019) modifications") %>% 
           pull(influence_rate)) 

```

## Estimate location of modes

```{r}

locmodes(data_IA_AMP_types$influence_rate, mod0 = 2)

```

## Reviewer Request: awareness vs. response confusion matrix 

```{r}

data_trial_level_valence_ia_amp %>%
  filter(IA_AMP_domain == "Valence") %>%
  mutate(consistent_rating = case_when(prime_type == "Negative" & rating == 0 ~ 1,
                                       prime_type == "Positive" & rating == 1 ~ 1,
                                       TRUE ~ 0)) %>%
  select(consistent_rating, influenced, experiment) %>%
  table()
   
```

# Session info

```{r}

sessionInfo()

```

