---
title: "Study 2"
subtitle: "Analyses"
author: "Ian Hussey & Jamie Cummins"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---
# Notes

1. H2 and H3 from experiment 1 were discarded as they were not relevant to our questions in this experiment, but could notionally be assessed in retrospect (i.e., Correlation between online and offline measures of influence, 
Contribution of offline and online measures in predicting AMP effect sizes).

```{r include=FALSE}

knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE, 
                      echo = FALSE)

```

```{r setup, message=FALSE, warning=FALSE, echo=FALSE}

# dependencies
library(tidyverse)
library(lme4)
library(sjPlot)
library(effects)
library(DescTools)
library(Rmisc)
library(effsize)
library(psych)
library(broom)
library(kableExtra)
# devtools::install_github("ianhussey/timesavers")  
library(timesavers)  # for round_df()
library(plotrix)


# get data 
task_level_data <- read.csv("../data/processed/processed_data.csv")

trial_level_amp_data <- read.csv("../data/processed/trial_level_amp_positive_negative_data.csv")

trial_level_ia_amp_data <- read.csv("../data/processed/trial_level_ia_amp_positive_negative_data.csv") %>%
  mutate(influenced = as.numeric(influenced))


# exclusions
task_level_data_exclusions <- task_level_data %>%
  filter(self_exclusion_1 == "Yes, use my data" & complete_data == TRUE)

trial_level_amp_data_exclusions <- trial_level_amp_data %>%
  filter(self_exclusion_1 == "Yes, use my data" & complete_data == TRUE)

trial_level_ia_amp_data_exclusions <- trial_level_ia_amp_data %>%
  filter(self_exclusion_1 == "Yes, use my data" & complete_data == TRUE)

```

# Demographics

Analytic sample after exclusions.

```{r age and gender}

# Gender
task_level_data_exclusions %>%
  mutate(gender = tolower(gender)) %>%
  dplyr::count(gender)

# Age mean and SD
task_level_data_exclusions %>%
  mutate(age = as.numeric(as.character(age))) %>%
  summarise("age (mean)" = mean(age), "age (standard deviation)" = sd(age)) %>%
  round_df(2)

```

# Manipulation checks

## M1: Demonstate an AMP effect on the AMP

### Fit model

```{r}

# fit model
model_m1 <- glmer(rating ~ prime_type + (1 | subject), 
                  family = binomial(link = "logit"),
                  data = trial_level_amp_data_exclusions)

# plot
plot_model(model_m1, type = "pred", terms = c("prime_type"))

# results table
tab_model(model_m1, emph.p = FALSE, ci.hyphen = ", ")

# extract OR
OR_m1 <- exp(cbind(est=fixef(model_m1), 
                   confint(model_m1, parm="beta_", method="Wald")))

# convert OR to D
abs(timesavers::OR_to_d(OR_m1))

```


## M2: Demonstate an AMP effect on the IA-AMP

### Fit model

```{r}

# fit model
model_m2 <- glmer(rating ~ prime_type + (1 | subject), 
                  family = binomial(link = "logit"),
                  data = trial_level_ia_amp_data_exclusions)

# plot
plot_model(model_m2, type = "pred", terms = c("prime_type"))

# results table
tab_model(model_m2, emph.p = FALSE, ci.hyphen = ", ")

# extract OR
OR_m2 <- exp(cbind(est=fixef(model_m2), 
                   confint(model_m2, parm="beta_", method="Wald")))

# convert OR to D
abs(timesavers::OR_to_d(OR_m2))

```


# Hypothesis tests

## H1: IA-AMP influence rate predicts IA-AMP effect

### H1a: at the trial level

Does conscious awareness of influence of the prime on the target moderate the AMP effect?

Key effect: influence*prime_type interaction

#### Fit model

```{r}

# model
model_h1a <- glmer(rating ~ influenced * prime_type + (1 | subject), 
                   family = binomial(link = "logit"),
                   data = trial_level_ia_amp_data_exclusions)

# plot
plot_model(model_h1a, type = "pred", terms = c("influenced", "prime_type"))

# results table
tab_model(model_h1a, emph.p = FALSE, ci.hyphen = ", ")

# extract OR
OR_h1a <- exp(cbind(est=fixef(model_h1a), 
                   confint(model_h1a, parm="beta_", method="Wald")))

# convert OR to D
abs(timesavers::OR_to_d(OR_h1a))

```

### H1b: at the participant level

Does rate of influence in the IA-AMP predict IA-AMP effects?

If effects in the IA-AMP are driven by intentional responding, then the size of the effect in the IA-AMP should be moderated by the subset of participants who are more often influenced by the primes. 

#### Fit model

```{r}

# model
fit_h1b <- lm(IA_AMP_effect_positive_negative ~ influence_rate, 
              data = task_level_data_exclusions)

# plot
ggplot(task_level_data_exclusions, aes(influence_rate, IA_AMP_effect_positive_negative)) + 
  geom_jitter(alpha = 0.3) +
  geom_rug(position = "jitter") +
  geom_smooth(method = lm) +
  labs(title = "Proportion of influenced trials and IA-AMP effect", 
       x = "Proportion of influenced trials", 
       y = "IA-AMP effect") +
  theme_classic()

# results table
tab_model(fit_h1b, emph.p = FALSE, ci.hyphen = ", ", show.std = TRUE)

```

## H2: IA-AMP influence rate predicts the absolute magnitude of the standard AMP effect

If effects in the standard AMP, as well as the IA-AMP, are driven by participants who are more often influenced, then rate of influence in the IA-AMP should predict effect sizes in the standard AMP. 

Because the AMP is completed prior to the IA AMP, if the IA AMP's influence rate predicts the (previously completed) AMP's effect then this implies that 1) measuring the influence rate does not perturb the IA AMP effect, and 2) that the rate of influence is reliable within participants across AMP/IA AMPs.

```{r}

# model
fit_h2 <- lm(abs(IA_AMP_effect_positive_negative) ~ influence_rate, 
             data = task_level_data_exclusions)

# plot
ggplot(task_level_data_exclusions, aes(influence_rate, abs(IA_AMP_effect_positive_negative))) + 
  geom_jitter(alpha = 0.3) +
  geom_rug(position = "jitter") +
  geom_smooth(method = lm) +
  labs(title = "Rate of influence and Standard AMP effect size", 
       x = "Rate of influence", 
       y = "Standard AMP effect size") +
  theme_classic()

# table
tab_model(fit_h2, emph.p = FALSE, ci.hyphen = ", ", show.std = TRUE)

```


## H3: Magnitude of Standard AMP effect compared to the IA-AMP effect (using uninfluenced trials only)

If intentional responding drives the AMP effect, then the effect size in the IA-AMP when only accounting for trials registered as 'unintentional' should be smaller than the effect size in the standard AMP.

```{r}

# subset data
subset <- task_level_data_exclusions %>%
  select(AMP_effect_positive_negative, IA_AMP_uninfluenced_effect_positive_negative) %>%
  na.omit()

# descriptives
subset %>%
  gather() %>%
  group_by(key) %>%
  dplyr::summarize(mean = mean(value),
                   sd = sd(value),
                   se = std.error(value),
                   ci_lwr = mean - se*1.96,
                   ci_upr = mean + se*1.96) %>%
  round_df(2)
  
# gather subset
long_subset <- subset %>%
  gather(condition, score, AMP_effect_positive_negative:IA_AMP_uninfluenced_effect_positive_negative)

# t test
t.test(score ~ condition, 
       paired = TRUE,
       data = long_subset) %>%
  tidy()

# cohen's d
effsize::cohen.d(score ~ condition,
       paired = TRUE,
       data = long_subset)

```
