---
title: "Study 4"
subtitle: "Analyses"
author: "Ian Hussey & Jamie Cummins"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# Notes

1. The numbering of hypotheses has changed between the preregistration and the analysis code here:
- H1 and H2 are now combined into a single hypothesis, with subhypotheses within this
- H2 in the code refers to H3 in the preregistration, H3 (code) to H4 (prereg), 
- and H4 (code) to H5 (prereg).

```{r include=FALSE}

knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)

```

```{r setup, message=FALSE, warning=FALSE}

# dependencies
library(tidyverse)
library(lme4)
library(sjPlot)
library(effects)
library(DescTools)
library(Rmisc)
library(effsize)
library(psych)
library(broom)
library(kableExtra)
# devtools::install_github("ianhussey/timesavers")  
library(timesavers)  # for round_df()
library(bootES)
library(metafor)
library(ggridges)

# get data 
task_level_data <- read.csv("../data/processed/processed_data.csv")

trial_level_politics_ia_amp_data <- read.csv("../data/processed/trial_level_ia_amp_obama_trump_data.csv") %>%
  filter(party %in% c("democrat", "republican")) %>%
  mutate(as.numeric(influenced))

trial_level_posneg_ia_amp_data <- read.csv("../data/processed/trial_level_ia_amp_positive_negative_data.csv") %>%
  filter(party %in% c("democrat", "republican")) %>%
  mutate(influenced = as.numeric(influenced))


# exclusions
task_level_data_exclusions <- task_level_data %>%
  filter(self_exclusion_1 == "Yes, use my data" & 
           complete_data == TRUE & 
           party %in% c("democrat", "republican"))

trial_level_politics_ia_amp_data_exclusions <- trial_level_politics_ia_amp_data %>%
  filter(self_exclusion_1 == "Yes, use my data" & 
           complete_data == TRUE & 
           party %in% c("democrat", "republican"))

trial_level_posneg_ia_amp_data_exclusions <- trial_level_posneg_ia_amp_data %>%
  filter(self_exclusion_1 == "Yes, use my data" & 
           complete_data == TRUE & 
           party %in% c("democrat", "republican"))

```

# Demographics

Analytic sample after exclusions.

```{r age and gender}

# count by party
task_level_data_exclusions %>%
  dplyr::count(party)

# Gender
task_level_data_exclusions %>%
  mutate(gender = tolower(gender)) %>%
  dplyr::count(gender)

# Age mean and SD
task_level_data_exclusions %>%
  filter(!(is.na(age))) %>%
  mutate(age = as.numeric(as.character(age))) %>%
  dplyr::summarise("age (mean)" = mean(age), 
                   "age (standard deviation)" = sd(age)) %>%
  round_df(2)

```

# Manipulation checks

## M1: Demonstate an AMP effect on the positive negative IA AMP

### Fit model

```{r}

# fit model
model_m1 <- glmer(rating ~ prime_type + (1 | subject), 
                  family = binomial(link = "logit"),
                  data = trial_level_posneg_ia_amp_data_exclusions)

# plot
plot_model(model_m1, type = "pred", terms = c("prime_type"))

# results table
tab_model(model_m1, emph.p = FALSE, ci.hyphen = ", ")

# extract OR and convert to d using the method proposed by Hasselblad & Hedges (1995, Equation 5, p. 170): d = log(OR)*(sqrt(3)/pi). See also Sánchez-Meca, Marín-Martínez & Chacón-Moscoso's (2003).
coefficients_temp <- summary(model_m1)$coefficients %>%
  as.data.frame() %>%
  rownames_to_column(var = "effect") %>%
  filter(effect == "prime_typeprime_type_B")

m1_d <- c(exp(pull(coefficients_temp, Estimate)), 
          exp(pull(coefficients_temp, Estimate) - pull(coefficients_temp, "Std. Error")*1.96),
          exp(pull(coefficients_temp, Estimate) + pull(coefficients_temp, "Std. Error")*1.96)) %>%
  timesavers::OR_to_d(.) %>%
  round(2)

```

OR converted to Cohen's d for familiarity: d = `r m1_d[1]`, 95% CI [`r m1_d[2]`, `r m1_d[3]`].

## M2: Demonstate an AMP effect on the politics IA AMP

### Fit model

```{r}

# fit model
model_m2 <- glmer(rating ~ prime_type * party + (1 | subject), 
                  family = binomial(link = "logit"),
                  data = trial_level_politics_ia_amp_data_exclusions)

# plot
plot_model(model_m2, type = "int")

# results table
tab_model(model_m2, emph.p = FALSE, ci.hyphen = ", ")

# extract OR and convert to d using the method proposed by Hasselblad & Hedges (1995, Equation 5, p. 170): d = log(OR)*(sqrt(3)/pi). See also Sánchez-Meca, Marín-Martínez & Chacón-Moscoso's (2003).
coefficients_temp <- summary(model_m2)$coefficients %>%
  as.data.frame() %>%
  rownames_to_column(var = "effect") %>%
  filter(effect == "prime_typeprime_type_B")

m2_d <- c(exp(pull(coefficients_temp, Estimate)), 
          exp(pull(coefficients_temp, Estimate) - pull(coefficients_temp, "Std. Error")*1.96),
          exp(pull(coefficients_temp, Estimate) + pull(coefficients_temp, "Std. Error")*1.96)) %>%
  timesavers::OR_to_d(.) %>%
  round(2)

```

OR converted to Cohen's d for familiarity: d = `r m2_d[1]`, 95% CI [`r m2_d[2]`, `r m2_d[3]`].


# Hypothesis tests

## H1: Does IA-AMP influence-awareness predict AMP effects in the same IA-AMP

### H1a: Politics IA-AMP

#### 1: at the trial level

Does conscious awareness of influence of the prime on the target moderate the AMP effect?

Key effect: influence:prime_type:party interaction

##### Fit model

```{r}

# model
model_h1a_1 <- glmer(rating ~ influenced * prime_type * party + (1 | subject), 
                     family = binomial(link = "logit"),
                     data = trial_level_politics_ia_amp_data_exclusions)

# plot
plot_model(model_h1a_1, type = "int")

# results table
tab_model(model_h1a_1, emph.p = FALSE, ci.hyphen = ", ", digits = 5)

# extract OR and convert to d using the method proposed by Hasselblad & Hedges (1995, Equation 5, p. 170): d = log(OR)*(sqrt(3)/pi). See also Sánchez-Meca, Marín-Martínez & Chacón-Moscoso's (2003).
coefficients_temp <- summary(model_h1a_1)$coefficients %>%
  as.data.frame() %>%
  rownames_to_column(var = "effect") %>%
  filter(effect == "influenced:prime_typeprime_type_B:partyrepublican")

h1a_1_d <- c(exp(pull(coefficients_temp, Estimate)), 
             exp(pull(coefficients_temp, Estimate) - pull(coefficients_temp, "Std. Error")*1.96),
             exp(pull(coefficients_temp, Estimate) + pull(coefficients_temp, "Std. Error")*1.96)) %>%
  timesavers::OR_to_d(.) %>%
  round(2)

```

OR converted to Cohen's d for familiarity: d = `r h1a_1_d[1]`, 95% CI [`r h1a_1_d[2]`, `r h1a_1_d[3]`].

#### 2: at the participant level

Does rate of influence in the IA-AMP predict IA-AMP effects?

If effects in the IA-AMP are driven by intentional responding, then the size of the effect in the IA-AMP should be moderated by the subset of participants who are more often influenced by the primes. 

##### Fit model

```{r}

# model
fit_h1b_2 <- lm(abs(IA_AMP_effect_obama_trump) ~ influence_rate_obama_trump, 
                data = task_level_data_exclusions)

# plot
ggplot(task_level_data_exclusions, aes(influence_rate_obama_trump, 
                                       abs(IA_AMP_effect_obama_trump))) + 
  geom_jitter(alpha = 0.3) +
  geom_rug(position = "jitter") +
  geom_smooth(method = lm) +
  labs(title = "Proportion of influenced trials and politics IA-AMP effect", 
       x = "Proportion of influenced trials\non the politics IA-AMP", 
       y = "Absolute politics IA-AMP effect") +
  theme_classic()

# results table
tab_model(fit_h1b_2, emph.p = FALSE, ci.hyphen = ", ")

```


### H1b: Positive-Negative IA-AMP

#### 1. At the trial level

Does conscious awareness of influence of the prime on the target moderate the AMP effect?

Key effect: influence*prime_type interaction

##### Fit model

```{r}

# model
model_h1b_1 <- glmer(rating ~ influenced * prime_type + (1 | subject), 
                     family = binomial(link = "logit"),
                     data = trial_level_posneg_ia_amp_data_exclusions)

# plot
plot_model(model_h1b_1, type = "pred", terms = c("influenced", "prime_type"))

# results table
tab_model(model_h1b_1, emph.p = FALSE, ci.hyphen = ", ")

# extract OR and convert to d using the method proposed by Hasselblad & Hedges (1995, Equation 5, p. 170): d = log(OR)*(sqrt(3)/pi). See also Sánchez-Meca, Marín-Martínez & Chacón-Moscoso's (2003).
coefficients_temp <- summary(model_h1b_1)$coefficients %>%
  as.data.frame() %>%
  rownames_to_column(var = "effect") %>%
  filter(effect == "influenced:prime_typeprime_type_B")

h1b_1_d <- c(exp(pull(coefficients_temp, Estimate)), 
             exp(pull(coefficients_temp, Estimate) - pull(coefficients_temp, "Std. Error")*1.96),
             exp(pull(coefficients_temp, Estimate) + pull(coefficients_temp, "Std. Error")*1.96)) %>%
  timesavers::OR_to_d(.) %>%
  round(2)

```

OR converted to Cohen's d for familiarity: d = `r h1b_1_d[1]`, 95% CI [`r h1b_1_d[2]`, `r h1b_1_d[3]`].

#### 2. At the participant level

Does rate of influence in the IA-AMP predict IA-AMP effects?

If effects in the IA-AMP are driven by intentional responding, then the size of the effect in the IA-AMP should be moderated by the subset of participants who are more often influenced by the primes. 

##### Fit model

```{r}

# model
fit_h1b_2 <- lm(IA_AMP_effect_positive_negative ~ influence_rate_positive_negative, 
                data = task_level_data_exclusions)

# plot
ggplot(task_level_data_exclusions, aes(influence_rate_positive_negative, 
                                       IA_AMP_effect_positive_negative)) + 
  geom_jitter(alpha = 0.3) +
  geom_rug(position = "jitter") +
  geom_smooth(method = lm) +
  labs(title = "Proportion of influenced trials and positive-negative IA-AMP effect", 
       x = "Proportion of influenced trials\non the positive-negative IA-AMP", 
       y = "Positive-negative IA-AMP effect") +
  theme_classic()

# results table
tab_model(fit_h1b_2, emph.p = FALSE, ci.hyphen = ", ")

```

## H2: Influence rate in one IA-AMP predicts the absolute magnitude of the other IA-AMP effect

If effects in the AMPs are driven by participants who are more often influenced, then rate of influence in one IA-AMP should predict effect sizes in the other. 

### H2a: Politics influence rate, pos-neg effect size

```{r}

# model
fit_h2a <- lm(abs(IA_AMP_effect_positive_negative) ~ influence_rate_obama_trump, 
              data = task_level_data_exclusions)

# plot
ggplot(task_level_data_exclusions, aes(influence_rate_obama_trump, 
                                       abs(IA_AMP_effect_positive_negative))) + 
  geom_jitter(alpha = 0.3) +
  geom_rug(position = "jitter") +
  geom_smooth(method = lm) +
  labs(title = "Rate of influence in the politics IA-AMP and positive-negative IA-AMP effect size", 
       x = "Politics IA-AMP influence rate", 
       y = "Positive-negative IA-AMP effect size") +
  theme_classic()

# table
tab_model(fit_h2a, emph.p = FALSE, ci.hyphen = ", ", show.std = TRUE)

```

### H2b: Pos-neg influence rate, politics effect size

If the positive-negative IA AMP's influence rate predicts the (previously completed) politics IA-AMP's effect then this implies that the rate of influence is reliable within participants/across IA AMPs.

Here we use the absolute politics AMP effect size, as the effects are necessarily opposite for Republicans and Democrats. Hence, we use absolute values as we are only interested in magnitude, not direction, of the effect.


```{r}

# model
fit_h2b <- lm(abs(IA_AMP_effect_obama_trump) ~ influence_rate_positive_negative, 
              data = task_level_data_exclusions)

# plot
ggplot(task_level_data_exclusions, aes(influence_rate_positive_negative, 
                                       abs(IA_AMP_effect_obama_trump))) + 
  geom_jitter(alpha = 0.3) +
  geom_rug(position = "jitter") +
  geom_smooth(method = lm) +
  labs(title = "Rate of influence in the positive-negative IA-AMP and politics IA-AMP effect size", 
       x = "Positive-negative IA-AMP influence rate", 
       y = "Politics IA-AMP effect size") +
  theme_classic()

# table
tab_model(fit_h2b, emph.p = FALSE, ci.hyphen = ", ", show.std = TRUE)

```

## H3: Influence-awareness rate correlates between IA-AMPs across different domains

If the subset of participants who respond intentionally in the AMP are consistent across procedures, then then influence rates in the AMP should correlate.

```{r fig.height=6, fig.width=6}

# test 
cor.test(task_level_data_exclusions$influence_rate_obama_trump,
         task_level_data_exclusions$influence_rate_positive_negative,
         paired = TRUE) %>% 
  tidy()

# plot
ggplot(task_level_data_exclusions, 
       aes(influence_rate_obama_trump, influence_rate_positive_negative)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(x = "Influence-awareness rate\nin politics IA-AMP", y = "Influence-awareness rate\nin positive-negative IA-AMP") +
  theme_classic() +
  ylim(0,1) +
  xlim(0,1)

```

## H4: The politics IA-AMPs ability to predict political affiliation is driven by the subset of trials on which participants reporting being influenced

### Group membership predicting AMP effect from influenced trials

```{r}

refactored_influenced <- task_level_data_exclusions %>% 
  select(IA_AMP_effect_obama_trump_influenced, party) %>%
  na.omit() %>%
  mutate(party = as.factor(as.character(party))) # need to refactor party as it thought it had 3 levels

# test
t.test(IA_AMP_effect_obama_trump_influenced ~ party,
       data = refactored_influenced, var.equal = TRUE)

# Cohen's d
d_inf <- effsize::cohen.d(IA_AMP_effect_obama_trump_influenced ~ party,
                          data = refactored_influenced)

d_inf

```

### Group membership predicting AMP effect from uninfluenced trials

```{r}

refactored_uninfluenced <- task_level_data_exclusions %>% 
  select(IA_AMP_effect_obama_trump_uninfluenced, party) %>%
  na.omit() %>%
  mutate(party = as.factor(as.character(party))) 

# test
t.test(IA_AMP_effect_obama_trump_uninfluenced ~ party,
       data = refactored_uninfluenced, var.equal = TRUE)

# Cohen's d
d_uninf <- effsize::cohen.d(IA_AMP_effect_obama_trump_uninfluenced ~ party,
                            data = refactored_uninfluenced)

d_uninf

```

### Chi square test to compare

Easiest implementation to compare two cohen's d values is to use the chi square (test for heterogeneity) from the metafor package. Might seem odd to fit a meta analysis here, but it's the easiest implementation of the test. Only the test for heterogeneity should be reported.

```{r}

data <- data.frame(yi = c(d_inf$estimate, d_uninf$estimate),
                   sei = c((d_inf$conf.int["upper"] - d_inf$conf.int["lower"])/(2*1.96),
                           (d_uninf$conf.int["upper"] - d_uninf$conf.int["lower"])/(2*1.96)),
                   condition = c("influenced", "uninfluenced")) %>%
  mutate(vi = sei^2)

fit <- rma(yi = yi,
           sei = sei,
           data = data,
           slab = condition)

#forest(fit)

# Q test in meta analysis heterogeneity is exactly equivalent to the below method
summary(fit, digits = 7)

```

#### Plot

```{r}

data_plotting <- 
  task_level_data_exclusions %>%
  dplyr::rename("Influenced\ntrials" = IA_AMP_effect_obama_trump_influenced,
                "Uninfluenced\ntrials" = IA_AMP_effect_obama_trump_uninfluenced) %>%
  mutate(party = dplyr::recode(party,
                               "democrat" = "Democrat",
                               "republican" = "Republican")) %>%
  gather(influence, 
         IA_AMP_effect, 
         c("Influenced\ntrials", "Uninfluenced\ntrials"))

data_summary_plotting <- data_plotting %>%
  group_by(party, influence) %>%
  dplyr::summarize(IA_AMP_effect_mean = mean(IA_AMP_effect, na.rm = TRUE),
                   IA_AMP_effect_se = plotrix::std.error(IA_AMP_effect, na.rm = TRUE)) %>%
  ungroup()

ggplot() +
  stat_density_ridges(data = data_plotting,
                      aes(x = IA_AMP_effect,
                          y = influence, 
                          fill = as.factor(party),
                          color = as.factor(party)),
                      geom = "density_ridges_gradient",
                      bandwidth = 0.35,
                      jittered_points = TRUE, 
                      scale = 0.95, 
                      rel_min_height = 0.05,
                      point_shape = "|", 
                      point_size = 3, 
                      size = 0.25,
                      position = position_points_jitter(height = 0, width = 0, yoffset = -0.05)) +
  geom_errorbarh(data = data_summary_plotting,
                 aes(xmin = IA_AMP_effect_mean - IA_AMP_effect_se*1.96,
                     xmax = IA_AMP_effect_mean + IA_AMP_effect_se*1.96,
                     y = influence,
                     color = as.factor(party)),
                 height = 0.1,
                 position = position_nudge(y = -0.16, x = 0)) +
  geom_point(data = data_summary_plotting,
             aes(x = IA_AMP_effect_mean,
                 y = influence,
                 fill = as.factor(party),
                 color = as.factor(party)),
             position = position_nudge(y = -0.16, x = 0)) +
  scale_colour_viridis_d(begin = 0.3, end = 0.7, alpha = 1) +
  scale_fill_viridis_d(begin = 0.3, end = 0.7, alpha = 0.5) +
  theme_classic() +
  scale_x_continuous(breaks = c(-1.0, -0.5, 0.0, 0.5, 1.0),
                     labels = c("-1.0\n(Obama-bad/Trump-good)", "-0.5", "0.0", "0.5", "1.0\n(Obama-good/Trump-bad)")) +
  ylab("Influence-awareness") +
  xlab("Evaluation on IA-AMP") +
  labs(color = "Political party") + 
  labs(name = "Political party") +
  labs(fill = "Political party")

```
